\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{fullpage}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\newcommand{\projname}{{\tt FriendlyReminder}}

\title{{\tt FriendlyReminder}: \\Requirements specification}
\author{Lars Yencken {\tt <lars.yencken@gmail.com>}}
%\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle
\section{Introduction}
\subsection{Aim}

With today's busy lifestyles, many of us are so focused on our work that we neglect to maintain contact with close friends and family. For some this is a conscious lifestyle decision, but for others this state of affairs is not desirable. \projname{} aims to be a lifestyle aid which periodically sends reminders for us to keep in touch with those we care about, and also reminds us about important dates such as birthdays which come up.

\section{Requirements}

\subsection{Account management}
To maintain privacy and personal details, \projname{} must:
\begin{enumerate}
	\item Allow individual user accounts, authenticated by email and password.
	\item Allow password-less re-visiting of the site for use on private computers.
	\item Publicly commit to the following privacy policy. \projname{} will:
	\begin{enumerate}
		\item Take reasonable steps to ensure the privacy of user data.
		\item Never disclose email addresses or other private data to a third party unless required by law.
		\item Avoid sending unsolicited emails to the user, unless it concerns changes to their account.
		\item Disclose any known breaches of privacy if they happen.
	\end{enumerate}
\end{enumerate}

\subsection{Friend management}
In order to be able to provide timely reminders for individual friends, \projname{} must, on a per-user basis:
\begin{enumerate}
	\item Allow the association of one or more friends, by name.
	\item For each friend, maintain:
	\begin{enumerate}
		\item A history of when the friend was last interacted with.
		\item Custom alert dates for that friend, for example, a birthday.
		\item How often you would minimally like to be in contact with your friend.
	\end{enumerate}
\end{enumerate}

\subsection{Alerts}

\begin{enumerate}
\item 
\end{enumerate}

\end{document}